Robert C. Dunnell’s _Systematics in Prehistory_ at 50

### 2021-09-03 analysis/paper/paper.Rmd
update renv

```{r echo = FALSE}
# we put these here to make sure they are processed before the 
# Rmd is knit (https://books.ropensci.org/targets/files.html) so
# we have all the most current analysis before we see the figures
library(targets)

>>>>

```{r echo = FALSE, eval=TRUE}
# we put these here to make sure they are processed before the 
# Rmd is knit (https://books.ropensci.org/targets/files.html) so
# we have all the most current analysis before we see the figures
library(targets)
